\documentclass[10pt, a4paper]{letter}

\usepackage{url}

\signature{Paul Bartholomew}
\address{CAGB 420, City and Guilds Building\\South Kensington Campus\\Imperial College
  London\\London\\SW7 2AZ\\(+44) 7722 926 927\\\url{paul.bartholomew08@imperial.ac.uk}}

\begin{document}

\begin{letter}{Person\\Dyson}

  \opening{Dear Sir/Madam:}

  I am a Post-Doctoral Research Associate in the department of aeronautics, Imperial College London,
  and am writing in regards to the Aero-Acoustics Simulation Engineer position advertised through
  the UK Fluids Network.

  Since winning funding to undertake an Undergraduate Research Opportunities Programme (UROP)
  project with Dr. Marquis, I have been interested in working in the field of CFD.
  Upon completing my MEng degree in mechanical engineering I pursued a PhD during the course of
  which I developed a fully-coupled solver for the two-fluid model to study particle-laden flows.
  This allowed me to gain wide experience, not only in the inner workings of a CFD solver, but also
  in developing an improved velocity interpolation allowing our code to tackle more complex
  multiphase flows and leading to my first publication.

  Working as a PDRA, I have been able to apply my knowledge of CFD and software writing skills
  developed during my PhD to implement a Low Mach Number (LMN) solver in the high-order Incompact3D
  code.
  Although not the direction pursued, such a solver could be used for studying aero-acoustic
  processes, indeed the paper which was the starting point for the implementation was studying noise
  radiated by a jet using Lighthill's analogy.
  I was delighted to be able to continue this work, winning further funding to expand the
  variable-density capabilities of the LMN solver to simulate free-surface flows.
  As a PDRA I have also enjoyed being able to use my experience to advise the PhD students in my
  research group when they have difficulties.
  
  I am confident that my broad experience as a researcher in the field of CFD, working
  with/developing several research codes, makes me an excellent candidate for this position.
  I enclose my Curriculum Vitae and look forward to hearing from you.

  \closing{Yours faithfully,}
  
\end{letter}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
